We are not the 99 percent: quantifying asphericity in the distribution of Local Group satellites

### 2018-04-23 paper/paper.tex
caption

@@

\begin{figure*}
\centering
\includegraphics[width=0.48\textwidth]{input_illustris1dark_obs_M31_n_11.pdf}
\includegraphics[width=0.48\textwidth]{input_illustris1dark_obs_MW_n_11.pdf}
\caption{Scalars describing satellite shape around the LG galaxies for
  a fixed number of satellites $N_s$=11:
  plane width $w$ in physical units, $c/a$ ratio and $b/a$ ratio.
  Left: M31, rigth: MW. The square at the center are observations; the
2D histograms are the contour levels after randomizing $10^4$ the
satellite positions while keeping the radial distribution fixed; the
blue circles are the results from Illustris-1-Dark. For the M31 these
three results (observations, randomized observations and simulations)
seem to be in broad agreement, while for the MW the three results
clearly differ. The corresponding plots for Illustris-1 and ELVIS can
be found in Figures \ref{fig:all_plots_illustris1} and
\ref{fig:all_plots_elvis},
respectively. \label{fig:physical_illustris1dark}}    
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.48\textwidth]{input_illustris1dark_obs_M31_n_11_normed.pdf}
\includegraphics[width=0.48\textwidth]{input_illustris1dark_obs_MW_n_11_normed.pdf}
\caption{Same layout as Figure \ref{fig:physical}. 
  Each scalar
  quantity is recentered and normalized by the mean value and standard
  deviation from the $10^4$ randomizations. 
  The distribution from the randomization now has by definition a mean
of zero and standard deviation of one. 
The results for the width and $c/a$ ratio of MW satellites are more
than two standard deviations away from the mean. } 
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.30\textwidth]{normalized_width_n_dependence.pdf}
\includegraphics[width=0.30\textwidth]{normalized_ca_ratio_n_dependence.pdf}
\includegraphics[width=0.30\textwidth]{normalized_ba_ratio_n_dependence.pdf}
\caption{Results}
\end{figure*}

>>>>

\begin{figure*}
\centering
\includegraphics[width=0.30\textwidth]{normalized_width_n_dependence.pdf}
\includegraphics[width=0.30\textwidth]{normalized_ca_ratio_n_dependence.pdf}
\includegraphics[width=0.30\textwidth]{normalized_ba_ratio_n_dependence.pdf}
\caption{Normalized asphericity scalars from observations as a function
  of satellite number, $N_s$. Left: plane width; center: $c/a$ ratio;
  right: $b/a$ ratio. 
  The plane width and $c/a$ ratio for the MW is
  consistently consistently found beyond two standard
  deviations; M31 shows the opposite trend and is always found
  \emph{within} two standard deviations \label{fig:normalized_n}.} 
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.48\textwidth]{input_illustris1dark_obs_M31_n_11.pdf}
\includegraphics[width=0.48\textwidth]{input_illustris1dark_obs_MW_n_11.pdf}
\caption{Scalars describing satellite shape around the LG galaxies for
  a fixed number of satellites $N_s$=11:
  plane width $w$ in physical units, $c/a$ ratio and $b/a$ ratio.
  Left: M31, rigth: MW. The square at the center are observations; the
2D histograms are the contour levels after randomizing $10^4$ the
satellite positions while keeping the radial distribution fixed; the
blue circles are the results from Illustris-1-Dark. For the M31 these
three results (observations, randomized observations and simulations)
seem to be in broad agreement, while for the MW the three results
clearly differ. 
The corresponding plots for Illustris-1 and ELVIS are
in Figures \ref{fig:all_plots_illustris1} and
\ref{fig:all_plots_elvis},
respectively. \label{fig:physical_illustris1dark}}     
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.48\textwidth]{input_illustris1dark_obs_M31_n_11_normed.pdf}
\includegraphics[width=0.48\textwidth]{input_illustris1dark_obs_MW_n_11_normed.pdf}
\caption{Same layout as Figure \ref{fig:physical_illustris1dark}. 
  Each scalar
  quantity is recentered and normalized by the mean value and standard
  deviation from the $10^4$ randomizations. 
  The distribution from the randomizations (plots over the diagonal)
  now has by definition a mean of zero and standard deviation of one. 
The results for the width and $c/a$ ratio of MW satellites are more
than two standard deviations away from the mean. 
The corresponding plots for Illustris-1 and ELVIS are
in Figures \ref{fig:all_plots_illustris1} and
\ref{fig:all_plots_elvis},
respectively. \label{fig:normalized_illustris1dark}}     
\end{figure*}
